### 2020-01-15 README.Rmd
updated instructions on running Matlab commands.
updated matlab commands
updated msBalance.Rmd to call matlab preprocessing

### How to run the code
1. Alter `paths.m` in the main project directory to point to the correct data directory on your local machine.
1. Run the Matlab code to load .mat files and populate patient-level data
    * Run `m/loadData.m` to load source files and populate the `csv/` directory.
    * A future version of this could call the Matlab script from R if useful.
1. "knit" `R/msBalance.Rmd` to produce `R/msBalance.html`.

>>>>

### How to run the code
1. Alter `paths.m` in the main project directory to point to the correct data directory on your local machine. This should contain the files `AllConsolidatedData_CS.mat` and `AllConsolidatedData_MS.mat`
1. Also modify the `matlabCommand` string in paths.m. On Dr. McKay's machine, this string is `/Applications/MATLAB_R2019a.app/bin/matlab -nojvm -nodesktop -nosplash -r`
1. "knit" `R/msBalance.Rmd` to produce `R/msBalance.html`. This will call matlab to create intermediary files if they are missing.
